---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Adam Weaver"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Based on the help file, the ```datasaurus_dozen``` file contains 1846 rows of data and 3 columns of information stored per row. The variables included in the data frame are a "dataset" variable, which indicates which of the 13 datasets a particular row is from, and x and y values, so that each row can be place on a coordinate plane.

### Exercise 2


The following code allows us to first filter the total data in the ```datasaurus_dozen``` file to include just the ```dino``` data set, then plot y vs. x for the remaining data:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


As the name of the data set suggests, the ```dino``` dataset, when plotted, yields a graph that is of an image of a dinosaur.



The following code allows us to calculate the correlation coefficient between y and x for the ```dino``` dataset, which we stored as ```dino_data``` after filtering the original data for just the ```dino``` dataset in the previous code:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
Because the correlation coefficient is extremely close to zero, it appears there is no meaningful correlation between x and y for the ```dino``` dataset. Considering that the data is intended to plot the shape of a dinosaur, and not represent any particular function, that should not be surprising.


### Exercise 3

To plot the ```star``` dataset, we can use almost the same code as we did to plot the ```dino``` dataset, with the notable difference of replacing any mentions of the ```dino``` dataset with the ```star``` dataset to access the new, desired dataset. The following code is the result of doing just that:

```{r plot-star}

```

I'm some text, you should replace me with more meaningful text...

```{r cor-star}

```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}

```

```{r}

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)